SSA based global code motion of identical computations

### 2017-04-17 paper.tex
comments

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
Code size         &\% age	increase in codesize \\\hline
400.perlbench	  & 1.00 \\\hline
401.bzip2	  & 1.00 \\\hline
403.gcc	          & 1.01 \\\hline
429.mcf	          & 1.00 \\\hline
433.milc	  & 1.00 \\\hline
444.namd	  & 1.01 \\\hline
445.gobmk	  & 1.01 \\\hline
447.dealII	  & 1.01 \\\hline
450.soplex	  & 0.99 \\\hline
453.povray	  & 1.00 \\\hline
456.hmmer	  & 1.00 \\\hline
458.sjeng	  & 1.00 \\\hline
462.libquantum	  & 1.00 \\\hline
464.h264ref	  & 1.00 \\\hline
470.lbm	          & 1.00 \\\hline
471.omnetpp	  & 0.99 \\\hline
473.astar	  & 1.02 \\\hline
482.sphinx3	  & 1.00 \\\hline
483.xalancbmk	  & 0.99 \\\hline
    \end{tabular}
  \end{center}
  \caption{Change in code size with and without code-motion on SPEC2006 at -Ofast}
  \label{tab:code-size}
\end{table}

@@

>>>>

Spills are listed in Table~\cite{tab:spills}. Spills were reduced by an average of 2\% on the
\SPEC{} benchmark suite. This is a result of cost-model which limits the code-motion to those
candidates which do not increase the register pressure (except for loads Section~\cite{sec:cost-models},
overall spills still decreases.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
Code size         &\% age	increase in codesize \\\hline
400.perlbench	  & 1.00 \\\hline
401.bzip2	  & 1.00 \\\hline
403.gcc	          & 1.01 \\\hline
429.mcf	          & 1.00 \\\hline
433.milc	  & 1.00 \\\hline
444.namd	  & 1.01 \\\hline
445.gobmk	  & 1.01 \\\hline
447.dealII	  & 1.01 \\\hline
450.soplex	  & 0.99 \\\hline
453.povray	  & 1.00 \\\hline
456.hmmer	  & 1.00 \\\hline
458.sjeng	  & 1.00 \\\hline
462.libquantum	  & 1.00 \\\hline
464.h264ref	  & 1.00 \\\hline
470.lbm	          & 1.00 \\\hline
471.omnetpp	  & 0.99 \\\hline
473.astar	  & 1.02 \\\hline
482.sphinx3	  & 1.00 \\\hline
483.xalancbmk	  & 0.99 \\\hline
Grand total       & 1.00 \\\hline
    \end{tabular}
  \end{center}
  \caption{Change in code size with and without code-motion on SPEC2006 at -Ofast}
  \label{tab:code-size}
\end{table}

Code size remained almost the same as a result of code-motion as shown in Table~\cite{tab:code-size}.
Some bencmarks like 473.astar increased in code size by almost 2\%. This is because once the code-size
of a function decreases it becomes cheaper to inline. As we can see in Table-\cite{tab:stats}, four
more functions got inlined in 473.astar. Except for 447.dealII, 450.soplex, 482.sphinx3 and 483.xalancbmk
all other benchmarks got more functions inlined.

@@

Some useful statc metric are presented in Table~\cite{tab:stats}, which shows how code-motion
impacted important compiler optimizations like inlining and LICM. LICM removes loop invariant
code out of the loop. It may hoist the code to the loop's preheader or sink the code to loop's
post-dominator \cite{steven1997advanced}. As we can see number of instructions hoisted increased
significantly in several benchmarks, although number of instructions sunk did not change by much.
Number of inlined functiosn also improved for most benchmarks. In general when more functions
were inlined, more functions were deleted as in 400.perlbench, 445.gobmk.
